---
title: "Analysis for asymmetry: Cimpian, Brandone, and Gelman (2010) replication and extension"
output: html_notebook
---

```{r}
library(rwebppl)
library(tidyverse)
library(tidyboot)
library(knitr)
library(ggpirate)
library(viridis)
library(ggthemes)
library(brms)
library(lme4)
theme_set(theme_few())
```

## Load data

```{r}
df.c.prior <- read_csv("../data/cbg2010/asymmetry-prior-4-trials.csv")

df.c.asym <- read_csv("../data/cbg2010/novelGenerics-trials-medSplitAccidental.csv")  %>%
  mutate(stim_type = ifelse(stim_type == "disease", "accidental", stim_type))
```

## Interpretation data

```{r fig.height = 5}
df.c.int.bs <- df.c.asym %>%
  filter(trial_type == "implied_prevalence") %>%
  mutate(response = 100*response) %>%
  group_by(stim_type) %>%
  tidyboot_mean(column = response)

# save(df.c.int.bs,
#      file = "../paper/cached_results/cimpian-interpretations-95ci.RData")

df.c.int.bs %>%
  ungroup() %>%
  mutate(stim_property = factor(stim_property, 
                           levels =  with(df.c.int.bs, stim_property[order(-mean)])),
          "Property type" = factor(stim_type,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental"))) %>%
  ggplot(., aes( x = stim_property, y = mean, ymin = ci_lower, ymax = ci_upper, 
                 fill = `Property type`))+
  geom_col(position = position_dodge(), color = 'black')+
  geom_errorbar(position = position_dodge(), alpha = 0.3)+
  #geom_pirate(bars = F, violins = F, width_points = 0.2)+
  #coord_flip()+
  #scale_color_viridis(discrete = T)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        axis.title.x = element_blank())+
  ylab("Mean implied prevalence")

# df.c.int %>%
#   mutate(stim_property = factor(stim_property, 
#                            levels =  with(df.c.int.bs, stim_property[order(mean)]))) %>%
#   ggplot(., aes( x = stim_property, y = response, color = stim_property))+
#   geom_pirate(bars = F, violins = F, width_points = 0.2)+
#   coord_flip()+
#   scale_color_viridis(discrete = T)+
#   ylim(0, 1)
```

```{r}
df.c.int.bs %>%
  ggplot(., aes(x = mean))+
  geom_histogram( binwidth = 0.075)
```

## Endorsement data



```{r endorsement regression}
 df.c.endorsements <- df.c.asym %>%
    filter(trial_type == "truth_conditions") %>%
    mutate(stim_prevalence = as.numeric(stim_prevalence),
           stim_prevalence = (stim_prevalence - mean(stim_prevalence))  / 20)


# rs.lmer.endorse.prev.type <- glmer(response ~ stim_prevalence * stim_type + (1 | workerid), 
#       data = df.c.endorsements, family = 'binomial')

summary(rs.lmer.endorse.prev.type)

rs.brm.endorse.prev.type <- brm(response ~ stim_prevalence * stim_type + 
      (1 +  stim_type | workerid) + 
      (1 | stim_property),
    family = 'bernoulli',
    iter = 2000,
    chains = 2,
    cores = 2,
      data = df.c.endorsements)

# save(rs.brm.endorse.prev.type, 
#      file = "../paper/cached_results/cbg_results_brms.RData")
```


```{r}
df.c.endorse_by_prev <- df.c.asym %>%
    filter(trial_type == "truth_conditions") %>%
    mutate(stim_prevalence = as.numeric(stim_prevalence)) %>%
  group_by(stim_type, stim_prevalence) %>%
  tidyboot_mean(column = response)
  
```


```{r}
dodge_width <- 7

df.c.endorse_by_prev %>%
  mutate("Property type" = factor(stim_type,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental"))) %>%
  ggplot(., aes( x = stim_prevalence, y = mean, ymin = ci_lower,
                 ymax = ci_upper, fill = `Property type`,
                 color = `Property type`))+
  geom_line(position = position_dodge(dodge_width), alpha = 0.4,
            linetype = 3)+
  geom_linerange(position = position_dodge(dodge_width), alpha = 0.6,
                 size = 1)+
  geom_point(position = position_dodge(dodge_width),
             size = 2.5, shape = 21, color = 'black')+
  scale_fill_solarized()+
  scale_color_solarized()+
  ylab("Proportion endorse")+
  xlab("Referent prevalence")+
  scale_x_continuous(limits = c(0, 100), breaks = c(10,  30, 50, 70,90))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  theme(legend.position = c(0.8, 0.3))
```



```{r}
average_truth_conditions <- function(responses,prevalences){
  avePrev<-if (sum(responses)>0){
    sum(responses*prevalences)/sum(responses)
  } else {
    100
  }
  return(avePrev)
}


df.atc.subj <- df.c.asym %>%
  filter(trial_type == "truth_conditions") %>%
   mutate(stim_prevalence = as.numeric(stim_prevalence)) %>%
    group_by(workerid, stim_type) %>%
  summarise(response = average_truth_conditions(response,stim_prevalence)) 

df.atc.subj %>% 
  ggplot(., aes( x= stim_type, y = response))+
  geom_pirate(violins = F, bars = F)
```


```{r}
df.atc <- df.c.asym %>%
  filter(trial_type == "truth_conditions") %>%
   mutate(stim_prevalence = as.numeric(stim_prevalence)) %>%
    group_by(workerid, stim_type) %>%
  summarise(response = average_truth_conditions(response,stim_prevalence)) %>%
  ungroup() %>%
  group_by(stim_type) %>%
  tidyboot_mean(column = response)


dodge_width <- 0.8

bind_rows(
  df.c.int.bs %>% mutate(src = 'implied prevalence'),
  df.atc %>% mutate(src = 'truth conditions')
) %>%
  mutate("Property type" = factor(stim_type,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental")),
         src = factor(src, levels = c("truth conditions",
                                      "implied prevalence"))) %>%
  ggplot(., aes( x = `Property type`, y = mean, ymin = ci_lower,
                 ymax = ci_upper, fill = `Property type`, alpha = src))+
  geom_col(position = position_dodge(dodge_width), width = dodge_width,
           color = 'black')+
  geom_errorbar(position = position_dodge(dodge_width),
                 size = 1, width = 0.1)+
  scale_fill_solarized()+
  scale_alpha_manual(values = c(0.6, 1))+
  scale_y_continuous(limits = c(0, 100))+
  ylab("Average truth conditions")+
  guides(fill = F)+
  theme(axis.text.x = element_text(angle = 45, vjust =1 ,hjust = 1),
        legend.title = element_blank(),
        axis.title.x = element_blank())
  #scale_x_continuous(limits = c(0, 100), breaks = c(10,  30, 50, 70,90))+
  #scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))

# save(df.c.endorse_by_prev, df.c.int.bs, df.atc,
#      file = "../paper/cached_results/cbg_results.RData")
```



## Model predictions

```{r}
m.c.asym <- read_csv("../models/results/results-cimpian-L0-S1predict-byItem-structuredPrior_uncertain-semantics-nullDist_beta1_100_20000_burn10000_lag25_chain2.csv")


m.c.asym.int <- m.c.asym %>%
  filter(category == "posterior") %>%
  group_by(param, property) %>%
  summarize(val = mean(val)) %>%
  group_by(param) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val), cred_lower = hdi_lower(val))


m.c.asym.end <- m.c.asym %>%
  filter(type == "endorsement") %>%
  group_by(param, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val), cred_lower = hdi_lower(val))

```

```{r model speaker optiamlity}
m.c.asym %>%
  filter(type == "speakerOptimality") %>%
  ggplot(., aes(x = val))+
  geom_histogram()
```



```{r model endorsements}
dodge_width <-0.1
m.c.asym.end %>%
  mutate("Property type" = factor(param,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental"))) %>%
  ggplot(., aes( x = category, y = MAP, ymin = cred_lower,
                 ymax = cred_upper, fill = `Property type`,
                 color = `Property type`))+
  geom_line(position = position_dodge(dodge_width), alpha = 0.4,
            linetype = 3)+
  geom_linerange(position = position_dodge(dodge_width), alpha = 0.6,
                 size = 1)+
  geom_point(position = position_dodge(dodge_width),
             size = 2.5, shape = 21, color = 'black')+
  scale_fill_solarized()+
  scale_color_solarized()+
  ylab("Proportion endorse")+
  xlab("\n Referent prevalence")+
  #scale_x_continuous(limits = c(0, 100), breaks = c(10,  30, 50, 70,90))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  theme(legend.position = c(0.75, 0.27))
  #coord_fixed(ratio = 65)
```

```{r add iteration number and average truth conditions}
m.samp.i <- m.c.asym %>%
  filter(type == "endorsement") %>%
  mutate(parameter = paste(type, property, category, sep = "_")) %>%
  select(-type, -property, -category) %>%
  group_by(parameter) %>%
  mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
  ungroup() %>%
  separate(parameter, into = c("type","property", "prevalence"), sep= "_")

m.samp.atc <- m.samp.i %>%
  rowwise() %>%
  mutate(judgment = rbinom(n = 1, size = 1, prob = val)) %>%
  group_by(property, param, iteration) %>% 
  summarize(
    total_endorsements = sum(judgment),
    atc = ifelse(total_endorsements==0, 1, sum(judgment*as.numeric(prevalence)) / total_endorsements)
    )


m.samp.i %>%
  group_by(param, prevalence) %>%
  summarize(expval = mean(val))
            
            
  # select(-val) %>%
  # spread(prevalence)
  # 
  # #ungroup() %>%
  # group_by(param, property, iteration) %>%
  # mutate(norm_prob = val / sum(val),
  #        prevalence = as.numeric(prevalence)) %>%
  # summarize(ave_prev_score = sum(prevalence * norm_prob)) %>%
  # ungroup()

m.atc.summary <- m.samp.atc %>%
  group_by(param, property) %>%
  summarize(atc = mean(atc)) %>%
  group_by(param) %>%
  summarize(MAP = estimate_mode(atc),
            cred_upper = hdi_upper(atc),
            cred_lower = hdi_lower(atc))
```


```{r model asymmetry}
m.cbg.asym <- bind_rows(
  m.c.asym.int %>% mutate(src = "Implied"),
  m.atc.summary %>% mutate(src = "Endorsed")
)
dodge_width = 0.5
m.cbg.asym %>%
  mutate("Property type" = factor(param,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental")),
         src = factor(src, levels = c("Endorsed",
                                      "Implied"),
                      labels = c("Endorsed", "Implied"))) %>%
  ggplot(., aes( x = `Property type`, y = MAP, ymin = cred_lower,
                 ymax = cred_upper, fill = `Property type`, alpha = src))+
  geom_col(position = position_dodge(dodge_width), width = dodge_width,
           color = 'black')+
  geom_errorbar(position = position_dodge(dodge_width),
                 size = 1, width = 0.1)+
  scale_fill_solarized()+
  scale_alpha_manual(values = c(0.6, 1))+
  #scale_y_continuous(limits = c(0, 100))+
  ylab("Average prevalence")+
  guides(fill = F)+
  theme(axis.text.x = element_text(angle = 45, vjust =1 ,hjust = 1),
        legend.title = element_blank(),
        axis.title.x = element_blank()#,
        #legend.position = c(0.75, 0.9)
        )

save(m.cbg.asym, m.c.asym.end, 
     file = "../paper/cached_results/cbg_modelpredictions_alpha1_apriori.RData")

```


## Alternative *average truth conditions* calculations

Do ATC calculation across the population and bootstrap.

```{r}

df.atc.bs <- df.c.asym %>%
    group_by(stim_type) %>%
    tidyboot(summary_function = function(x) x %>% summarise(atc = average_truth_conditions(response,stim_prevalence)),
           statistics_functions = function(x) x %>%
           summarise_at(vars(atc), funs(ci_upper, mean, ci_lower))
           )

df.atc.bs
```


looks like the full bootstrap returns values appreciably below the subject-wise analysis. technically, i should be resampling participants...

### by participant resampling

```{r}
df.c.asym %>%
  filter(trial_type == "truth_conditions")  %>%
  select(stim_property, stim_prevalence) %>%
  table(.)
```


Bootstrapping subjects

```{r}
average_truth_conditions <- function(responses,prevalences){
  avePrev<-if (sum(responses)>0){
    (mean(responses)*prevalences)/sum(responses)
  } else {
    100
  }
  return(avePrev)
}


bootstrap_atc <- function(i){
  df.c.asym %>%
    filter(trial_type == "truth_conditions") %>%
    mutate(type_prev_response = paste(stim_type, "_",
                                      stim_property, "_", 
                                      stim_prevalence, "_", 
                                      response, sep="")) %>%
    select(workerid, trial_num, type_prev_response) %>%
    spread(trial_num, type_prev_response) %>%
    sample_n(40, replace = T) %>%
    gather(trial_num, val, -workerid) %>%
    separate(val, into = c("stim_type","property", "prevalence", "response"),
             sep = "_") %>%
    mutate(prevalence = as.numeric(prevalence),
           response = as.numeric(response)) %>%
    group_by(stim_type, property, prevalence) %>%
    summarize(prop_endorse = mean(response)) %>%
    ungroup() %>% 
    #group_by(stim_type) %>%
    group_by(stim_type, property) %>%
    mutate(endorse_prob = prop_endorse/ sum(prop_endorse)) %>%
    summarize(atc = sum(endorse_prob * prevalence),
              i = i)
}

df.c.asym.bs <- bind_rows(lapply(1:500, bootstrap_atc))
```

```{r}
df.c.asym.bs %>%
  ggplot(., aes( x = property, y = atc , color = stim_type))+
  geom_pirate(violins = F, bars = F)+
  theme(axis.text.x = element_text(angle =45, hjust =1, vjust =1))
```

```{r}
 df.c.asym %>%
   filter(trial_type == "truth_conditions")  %>%
   select(stim_property, stim_prevalence) %>%
   table(.)

 df.c.asym %>%
   filter(trial_type == "truth_conditions")  %>%
   select(stim_type, stim_prevalence) %>%
   table(.)

```

The data is pretty sparse on a by-item basis. For examples, "feathers" has a very low ATC, but also has very 


### BDA threshold model ? (doesn't work)

```{r}
bayesian_ave_truth_conditions <- '
var noisyThreshold = function(x, t, noise){
  Infer({model: function(){
    flip(noise) ? binomial({n:1, p: 0.5}) :
      x > t ? 1 : 0
  }})
}
 
var property_types = _.uniqBy(_.map(data, "stim_type"))

var model = function(){
  var noise = uniformDrift({a: 0, b: 1, width: 0.1});
  // var noise = uniformDraw(_.range(0, 1, 0.1))
  extend(_.fromPairs(map(function(property){
    var property_data = _.filter(data, {stim_type: property})
    // var threshold = uniformDrift({a: 0, b: 1, width: 0.1});
    var threshold = uniformDraw([0, 0.2, 0.4, 0.6, 0.8, 0.95])
    mapData({data: data}, function(d){
      observe(noisyThreshold(d.stim_prevalence / 100, threshold, noise), d.response)
    })
    return [property, threshold]
  }, property_types)), {noise})
}
'
```

```{r}
df.tc.data <- df.c.asym %>%
  filter(trial_type == "truth_conditions") %>%
   mutate(stim_prevalence = as.numeric(stim_prevalence)) %>%
  select(workerid, stim_type, stim_prevalence, response)

rs.wp.batc <- webppl(bayesian_ave_truth_conditions,
       model_var = "model",
       inference_opts = list(method = "MCMC", samples = 100,
                             burn = 50, verbose = T),
       #inference_opts = list(method = "enumerate"),
       data_var = "data",
       data = df.tc.data)
```

```{r}
rs.wp.batc %>%
  ggplot(., aes( x = value))+
  geom_histogram()+
  facet_wrap(~Parameter, scales = 'free')
```



### Need probabilities

```{r}
m.priors.i <- m.c.asym %>%
  filter(param == "prevWhenPresent") %>%
  mutate(parameter = paste(type, property, category, sep = "_")) %>%
  select(-type, -property, -category) %>%
  group_by(parameter) %>%
  mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
  ungroup() %>%
  separate(parameter, into = c("type","property", "param"), sep= "_") %>%
  spread(param, val) %>%
  mutate(
    need_0.1 = dbeta(0.1, shape1 = alpha, shape2 = beta),
    need_0.3 = dbeta(0.3, shape1 = alpha, shape2 = beta),
    need_0.5 = dbeta(0.5, shape1 = alpha, shape2 = beta),
    need_0.7 = dbeta(0.7, shape1 = alpha, shape2 = beta),
    need_0.9 = dbeta(0.9, shape1 = alpha, shape2 = beta)
    ) %>%
  gather(prev, need, starts_with("need")) %>%
  separate(prev, into=c("scrap", "prevalence"), sep = "_") %>%
  mutate(prevalence = as.numeric(prevalence))

m.priors.need.summary <- m.priors.i %>%
  group_by(property, prevalence) %>%
  summarize(need_map = estimate_mode(need),
            need_upper = hdi_upper(need),
            need_lower = hdi_lower(need))
```


```{r}
df.c.endorsements <- df.c.asym %>%
    filter(trial_type == "truth_conditions")


df.c.endorsements <- left_join(
  df.c.endorsements %>%
    mutate(stim_prevalence = as.numeric(stim_prevalence)), 
  m.priors.need.summary %>%
    mutate(stim_prevalence = prevalence*100) %>%
    select(-prevalence) %>%
    rename(stim_property = property)
)

bootstrap_need_aed <- function(i){
  df.c.endorsements %>%
    mutate(type_prev_need_response = paste(stim_type, "_",
                                      stim_property, "_", 
                                      stim_prevalence, "_", 
                                      need_map, "_",
                                      response, sep="")) %>%
    select(workerid, trial_num, type_prev_need_response) %>%
    spread(trial_num, type_prev_need_response) %>%
    sample_n(40, replace = T) %>%
    gather(trial_num, val, -workerid) %>%
    separate(val, into = c("stim_type","property", "prevalence", "need", "response"),
             sep = "_") %>%
    mutate(prevalence = as.numeric(prevalence),
           need = as.numeric(need),
           response = as.numeric(response)) %>%
    group_by(stim_type, property, prevalence, need) %>%
    summarize(prop_endorse = mean(response)) %>%
    ungroup() %>% 
    #group_by(stim_type, property) %>%
    group_by(stim_type) %>%
    mutate(
      endorse_posterior_uniform = prop_endorse / sum(prop_endorse),
      endorse_posterior = prop_endorse * need,
      endorse_posterior_normalized = endorse_posterior/ sum(endorse_posterior)) %>%
    summarize(aed = sum(endorse_posterior_normalized * prevalence),
              aed_uniform = sum(endorse_posterior_uniform * prevalence),
              i = i)
}

df.c.need_aed.bs <- bind_rows(lapply(1:500, bootstrap_need_aed))
```

```{r summarize need aed}
df.c.need_aed.bs.summary <- df.c.need_aed.bs %>%
  group_by(stim_type) %>%
  #group_by(stim_type, property) %>%
  summarize(mean = mean(aed, na.rm = T),
            ci_upper = quantile(aed, 0.975, na.rm = T),
            ci_lower = quantile(aed, 0.025, na.rm = T))
```

```{r}
dodge_width <- 0.8
df.c.int.bs <- df.c.asym %>%
  filter(trial_type == "implied_prevalence") %>%
  mutate(response = 100*response) %>%
  group_by(stim_type) %>%
  tidyboot_mean(column = response)

df.c.need_aed.int.bs <- bind_rows(
  df.c.int.bs %>% mutate(src = 'implied prevalence'),
  df.c.need_aed.bs.summary %>% mutate(src = 'truth conditions')
)

df.c.need_aed.int.bs %>%
  mutate("Property type" = factor(stim_type,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental")),
         src = factor(src, levels = c("truth conditions",
                                      "implied prevalence"))) %>%
  ggplot(., aes( x = `Property type`, y = mean, ymin = ci_lower,
                 ymax = ci_upper, fill = `Property type`, alpha = src))+
  geom_col(position = position_dodge(dodge_width), width = dodge_width,
           color = 'black')+
  geom_errorbar(position = position_dodge(dodge_width),
                 size = 1, width = 0.1)+
  scale_fill_solarized()+
  scale_alpha_manual(values = c(0.6, 1))+
  scale_y_continuous(limits = c(0, 100))+
  ylab("Average truth conditions")+
  guides(fill = F)+
  theme(axis.text.x = element_text(angle = 45, vjust =1 ,hjust = 1),
        legend.title = element_blank(),
        axis.title.x = element_blank())
  #scale_x_continuous(limits = c(0, 100), breaks = c(10,  30, 50, 70,90))+
  #scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))

save(df.c.need_aed.int.bs, df.c.need_aed.int.item.bs.summary,df.c.unif_aed.int.item.bs.summary,
     file = "../paper/cached_results/cbg_results_aedNeed.RData")
```

```{r item wise asymmetry with aed}
bootstrap_need_aed_property <- function(i){
  df.c.endorsements %>%
    mutate(type_prev_need_response = paste(stim_type, "_",
                                      stim_property, "_", 
                                      stim_prevalence, "_", 
                                      need_map, "_",
                                      response, sep="")) %>%
    select(workerid, trial_num, type_prev_need_response) %>%
    spread(trial_num, type_prev_need_response) %>%
    sample_n(40, replace = T) %>%
    gather(trial_num, val, -workerid) %>%
    separate(val, into = c("stim_type","property", "prevalence", "need", "response"),
             sep = "_") %>%
    mutate(prevalence = as.numeric(prevalence),
           need = as.numeric(need),
           response = as.numeric(response)) %>%
    group_by(stim_type, property, prevalence, need) %>%
    summarize(prop_endorse = mean(response)) %>%
    ungroup() %>% 
    group_by(stim_type, property) %>%
    #group_by(stim_type) %>%
    mutate(
      endorse_posterior_uniform = prop_endorse / sum(prop_endorse),
      endorse_posterior = prop_endorse * need,
      endorse_posterior_normalized = endorse_posterior/ sum(endorse_posterior)) %>%
    summarize(aed = sum(endorse_posterior_normalized * prevalence),
              aed_uniform = sum(endorse_posterior_uniform * prevalence),
              i = i)
}

df.c.need_aed.item.bs <- bind_rows(lapply(1:500, bootstrap_need_aed_property))

df.c.int.item.bs <- df.c.asym %>%
  filter(trial_type == "implied_prevalence") %>%
  mutate(response = 100*response) %>%
  group_by(stim_type, stim_property) %>%
  tidyboot_mean(column = response)

df.c.need_aed.item.bs.summary <- df.c.need_aed.item.bs %>%
  #group_by(stim_type) %>%
  group_by(stim_type, property) %>%
  summarize(aed_mean = mean(aed, na.rm = T),
            aed_upper = quantile(aed, 0.975, na.rm = T),
            aed_lower = quantile(aed, 0.025, na.rm = T)) %>%
  ungroup() %>% rename(stim_property = property)

df.c.unif_aed.item.bs.summary <- df.c.need_aed.item.bs %>%
  #group_by(stim_type) %>%
  group_by(stim_type, property) %>%
  summarize(aed_mean = mean(aed_uniform, na.rm = T),
            aed_upper = quantile(aed_uniform, 0.975, na.rm = T),
            aed_lower = quantile(aed_uniform, 0.025, na.rm = T)) %>%
  ungroup() %>% rename(stim_property = property)



df.c.need_aed.int.item.bs.summary<- left_join(
  df.c.int.item.bs,
  df.c.need_aed.item.bs.summary 
)

df.c.unif_aed.int.item.bs.summary<- left_join(
  df.c.int.item.bs,
  df.c.unif_aed.item.bs.summary 
)

df.c.unif_aed.int.item.bs.summary %>%
  mutate("Property type" = factor(stim_type,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental"))) %>%
  ggplot(., aes( x = aed_mean, xmin = aed_lower, 
                 xmax = aed_upper,
                 y = mean, ymin = ci_lower,
                 ymax = ci_upper, color = `Property type`))+
  geom_point()+
  geom_errorbar(alpha = 0.3)+
  geom_errorbarh(alpha = 0.3)+
  scale_fill_solarized()+
  scale_alpha_manual(values = c(0.6, 1))+
  #scale_y_continuous(limits = c(25, 100))+
  #scale_x_continuous(limits = c(25, 100))+
  geom_abline(intercept = 0, slope = 1)+
  #ylab("Average truth conditions")+
  guides(fill = F)+
  xlab("average endorsed prevalence")+
  ylab("average implied prevalence")
```


```{r}
with(df.c.need_aed.int.item.bs.summary, cor(aed_mean, mean))
```

